Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-08 document/ms.tex
what can future catalogs produce?

Given our domain knowledge of how detection efficiency depends on the physical
parameters, it might seem silly to measure the survey completeness in period
and radius instead of radius ratio or signal-to-noise.
It is also likely that a change of coordinates would yield a higher precision
result.
That being said, it is still correct to measure the completeness in period and
radius, and there are a few practical reasons for our choice.
First, since the radius uncertainties are dominated by uncertainties in the
stellar parameters, it is not possible to use the published catalog
(\citealt{petigura}) to compute constraints on radius ratios.
\dfmtodo{finish this}

>>>>

Given our domain knowledge of how detection efficiency depends on the physical
parameters, it might seem silly to measure the survey completeness in period
and radius instead of radius ratio or signal-to-noise.
It is also likely that a change of coordinates would yield a higher precision
result.
That being said, it is still correct to measure the completeness in period and
radius, and there are a few practical reasons for our choice.
The main argument is that since the radius uncertainties are dominated by
uncertainties in the stellar parameters, it is not possible to use the
published catalog (\citealt{petigura}) to compute constraints on radius
ratios.
In future catalogs, this problem would be solved by publishing representations
of the posterior probabilities that are being measured.
In this case, these parameters are radius ratio and stellar radius instead of
just the physical radius.
